Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2023-02-03 letters/response-ref-1-v1.tex

\vspace{5mm}
The event times~$T_i$ depend heavily on the event intensity function~$h_i (t;\theta)$ and will not be guaranteed to be uniformly spread across points in $[0,\tau]$.  The subsampling times~$D_i$ depend on the subsampling intensity function~$\pi_i(t)$ and
\vspace{5mm}

\item {\it Add a plot of the mean, covariance functions for $y=0$ and $y=1$.}

\vspace{5mm}
We have added mean and covariance functions to the supplementary materials as suggested.  The plots demonstrate distinct behavior in the means for $y=0$ and $y=1$; while the covariance functions are XXXX.
\vspace{5mm}

\item {\it Page 9, line 6, isn’t the integral in (2) $\int_{t-\Delta}^t X(s) \beta(s)ds$? The whole development assumes the integral to be $\int_{t-\Delta}^t X(t-s) \beta(s)ds$. The interpretation of the coefficient function $\beta()$ would be different for two cases. Please clarify.}

@@

\end{enumerate}

\newpage

{\bf Response to Reviewer \#2}

I am incredibly grateful for this review.  I am very happy that the referee found that this paper makes a nice contribution to the field of functional data; we, of course, agree. The application was what drove this methodology so we are also happy to hear that the referee found the application interesting. We next address the reviewers specific comments.

\begin{enumerate}
\item {\it There exists a good amount of recent efforts modeling event data with functional data predictor or joint modeling, so a literature review on relevant papers would be useful. See, for example, papers by Dr. Ciprian Crainiceanu from Johns Hopkins, Dr. Sheng Luo from Duke, and Dr. Jiguo Cao from Simon Fraser.}

\vspace{5mm}
XXXXXX.
We added Section XX to describe the related work and connect our methodology to the existing literature.
\vspace{5mm}
\end{enumerate}

### 2023-02-03 write-up/letters/cover letter-fda-recurrentevents.tex

Kindly find enclosed the revised version of the manuscript ID JCGS-22-236, "Recurrent event analysis in the presence of real-time high frequency data via random subsampling."   We have revised the article to address the referees’ requests.  The reports called for a major revision to include related work on modeling event data with functional data predictors as well as historical functional linear models, include empirical evidence and associated discussion of the computational benefits of our proposal, as well as clarify several technical details in the theoretical sections and provide important intuition/sketches of the proofs. The new version complies with these requests.

We believe the work presents an important advance that gives researchers a simple tool to analyze recurrent event data in the presence of high-frequency sensors data.  Attached please find a detailed response to the referees outlining how the changes to the manuscript address the concerns raised in their reports.

>>>>

Kindly find enclosed the manuscript titled ``Recurrent Event Analysis in the Presence of Real-time High Frequency Data via Random Subsampling.''  This manuscript is motivated by digital monitoring studies that collect real-time high frequency data via mobile sensors and their use in the analysis of recurrent event outcomes such as smoking, drug use, alcohol use, or self-identified moments of suicide ideation. Likelihood calculations for the recurrent event analysis become computationally prohibitive in this setting. A random subsampling framework is proposed for computationally efficient, approximate likelihood-based estimation which is shown to be equivalent to penalized logistic regression estimation, allowing for standard, ``off-the-shelf'' software to be used in fitting these models. Simulations demonstrate the method and efficiency-computation trade-off. We end by illustrating our approach using data from a digital monitoring study of suicidal ideation.

We believe the work presents an important advance in how researchers should approach recurrent event analysis in settings in the present of real-time high frequency data such as in mobile health where sensor data is prevalent.
